NURM: a tool to locate numerical differences in pipelines

### 2019-11-29 paper.tex

\title{NURM: file-based localization of numerical /differences/ without instrumentation}

@@

% Reproducibility: crisis, numerical stability
% Containerization isn't the solution

% Complex neuroimaging pipelines
In neuroimaging, our primary application field, data analyses often consist
of computational pipelines aggregating heterogeneous codes to implement a
specific function. For instance ...

% Verificarlo and MCA, require recompilation
Numerical instabilities originate in the limited \todo{precision} of floating-point representations. 
Traditionnaly, it has been evaluated through

% -> File-based analysis of pipelines without instrumentation
% Reprozip

>>>>

\title{NURM: a tool to 
locate numerical differences in pipelines}

@@
